\sysfull

### 2018-08-06 paper/asplos19/intro.tex
update intro fig caption

Upon power failures, a device loses the volatile state in its registers, stack, SRAM, and retains the state of any non-volatile memory, such as FRAM. While capturing periodic checkpoints~\cite{mementos,quickrecall} and sleep scheduling~\cite{dewdrop,hibernus,hibernusplusplus} help preserve execution progress, failures can leave non-volatile state incorrect, partially updated. These inconsistencies cause intermittent execution to deviate from continuously-powered behavior, often leading to an unrecoverable application failure~\cite{dino,edb}. Prior work developed two main approaches to deal with data inconsistency for intermittently-powered devices: (i) \emph{software-based programming and execution models}~\cite{dino,ratchet,chain,alpaca} and (ii) \emph{hardware-based computer architecture support}~\cite{hicks_isca_2017,idetic,nvp}. Complex hardware architectural changes are expensive to design, verify, and manufacture. New hardware architectures are also inapplicable to existing systems~\cite{hicks_isca_2017,nvp}. Software approaches are simpler and applicable to existing devices today. Therefore, this work focuses on software approaches. In particular we address the key limitation of task-based programming and execution model, that is the {\em inflexibility} and \emph{energy-unawareness} of statically decomposing a program into tasks.
%
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/intro-figure.pdf}
    \caption{Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{C}) of individual tasks (denoted as \texttt{Tx}). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{figure}

>>>>

Upon power failures, a device loses the volatile state in its registers, stack, SRAM, and retains the state of any non-volatile memory, such as FRAM. While capturing periodic checkpoints~\cite{mementos,quickrecall} and sleep scheduling~\cite{dewdrop,hibernus,hibernusplusplus} help preserve execution progress, failures can leave non-volatile state incorrect, partially updated. These inconsistencies cause intermittent execution to deviate from continuously-powered behavior, often leading to an unrecoverable application failure~\cite{dino,edb}. Prior work developed two main approaches to deal with data inconsistency for intermittently-powered devices: (i) \emph{software-based programming and execution models}~\cite{dino,ratchet,chain,alpaca} and (ii) \emph{hardware-based computer architecture support}~\cite{hicks_isca_2017,idetic,nvp}. Complex hardware architectural changes are expensive to design, verify, and manufacture. New hardware architectures are also inapplicable to existing systems~\cite{hicks_isca_2017,nvp}. Software approaches are simpler and applicable to existing devices today. Therefore, this work focuses on software approaches. In particular we address the key limitation of task-based programming and execution model, that is the {\em inflexibility} and \emph{energy-unawareness} of statically decomposing a program into tasks.
%
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/intro-figure.pdf}
    \caption{Task coalescing reduces time and energy overhead by performing fewer commits (denoted as \texttt{C}) than the individual tasks (denoted as \texttt{Tx}) commits (left). On the other hand, task splitting reduces wasted computation and enables termination of big tasks, requiring more energy than the energy buffer can hold (right).}
    \label{fig:coalesce}
\end{figure}
